\LARGE Untangling the link between traits, size and growth rate in plants

### 2016-07-28 figure_conceptual.tex
Manuscript in subdirectory, all outputs in "output"

\defineRow{0}{thisrow}
\rowtitle{Biomass production}
\firstcol{1}{$\frac{\textrm{d}b}{\textrm{d}t}$}{figures/F2_mass_production_net_production}{}
\othercol{2}{$y$}{figures/empty_box}{$\times$}
\othercol{3}{$\Bigg(A$}{figures/F2_mass_production_assimilation}{-}
\othercol{4}{\ $R$}{figures/F2_mass_production_respiration}{$\Bigg)$}
\othercol{5}{$-T$}{figures/F2_mass_production_turnover}{}
\rowlabel{(1)}

\defineRow{1}{thisrow}
\rowtitle{Construction costs}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}m_{\textrm{t}}}$}{figures/F2_leaf_area_growth_leaf_fraction}{$\Bigg($}
\othercol{2}{$\frac{\textrm{d}m_{\textrm{l}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{+}
\othercol{3}{$\frac{\textrm{d}m_{\textrm{ss}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{+}
\othercol{4}{$\frac{\textrm{d}m_{\textrm{sb}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{+}
\othercol{5}{$\frac{\textrm{d}m_{\textrm{r}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{$\Bigg)^{-1}$}
 \rowlabel{(2)}

\defineRow{2}{thisrow}
\rowtitle{Leaf-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{figures/F2_leaf_area_growth_dleaf_area_dt}{}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}m_{\textrm{t}}}$}{figures/F2_leaf_area_growth_leaf_fraction}{$\times$}
\othercol{3}{$\frac{\textrm{d}m_{\textrm{t}}}{\textrm{d}b}$}{figures/F2_leaf_area_growth_leaf_fraction}{$\times$}
\othercol{4}{$\frac{\textrm{d}b}{\textrm{d}t}$}{figures/F2_leaf_area_growth_net_production}{}
\rowlabel{(3)}

\defineRow{3}{thisrow}
\rowtitle{Height growth}
\firstcol{1}{$\frac{\textrm{d}h}{\textrm{d}t}$}{figures/F2_height_growth_height_growth_rate}{}
\othercol{2}{$\frac{\textrm{d}h}{\textrm{d}a_{\textrm{l}}}$}{figures/F2_height_growth_dheight_dleaf_area}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{figures/F2_leaf_area_growth_dleaf_area_dt}{}
\rowlabel{(4)}

\defineRow{4}{thisrow}
\rowtitle{Basal-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{figures/F2_basal_growth_dbasal_area_dt}{}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{ss}}}{\textrm{d}a_{\textrm{l}}}$}{figures/empty_box}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{figures/F2_leaf_area_growth_dleaf_area_dt}{+}
\othercol{4}{$\frac{\textrm{d}a_{\textrm{sh}}}{\textrm{d}t}$}{figures/empty_box}{}
\rowlabel{(5)}

\defineRow{5}{thisrow}
\rowtitle{Diameter growth}
\firstcol{1}{$\frac{\textrm{d}D}{\textrm{d}t}$}{figures/F2_diameter_growth_dbasal_diam_dt}{}
\othercol{2}{$\frac{\sqrt{\pi}}{\sqrt{a_{\textrm{st}}}}$}{figures/empty_box}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{figures/F2_basal_growth_dbasal_area_dt}{}
\rowlabel{(6)}

>>>>

\defineRow{0}{thisrow}
\rowtitle{Biomass production}
\firstcol{1}{$\frac{\textrm{d}b}{\textrm{d}t}$}{output/F2_net_mass_production_dt_net_mass_production_dt}{}
\othercol{2}{$y$}{output/empty_box}{$\times$}
\othercol{3}{$\Bigg(A$}{output/F2_net_mass_production_dt_assimilation}{-}
\othercol{4}{\ $R$}{output/F2_net_mass_production_dt_respiration}{$\Bigg)$}
\othercol{5}{$-T$}{output/F2_net_mass_production_dt_turnover}{}
\rowlabel{(1)}

\defineRow{1}{thisrow}
\rowtitle{Construction costs}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}m_{\textrm{t}}}$}{output/F2_darea_leaf_dmass_live_darea_leaf_dmass_live}{$\Bigg($}
\othercol{2}{$\frac{\textrm{d}m_{\textrm{l}}}{\textrm{d}a_{\textrm{l}}}$}{output/F2_darea_leaf_dmass_live_dmass_leaf_darea_leaf}{+}
\othercol{3}{$\frac{\textrm{d}m_{\textrm{ss}}}{\textrm{d}a_{\textrm{l}}}$}{output/F2_darea_leaf_dmass_live_dmass_sapwood_darea_leaf}{+}
\othercol{4}{$\frac{\textrm{d}m_{\textrm{sb}}}{\textrm{d}a_{\textrm{l}}}$}{output/F2_darea_leaf_dmass_live_dmass_bark_darea_leaf}{+}
\othercol{5}{$\frac{\textrm{d}m_{\textrm{r}}}{\textrm{d}a_{\textrm{l}}}$}{output/F2_darea_leaf_dmass_live_dmass_root_darea_leaf}{$\Bigg)^{-1}$}
 \rowlabel{(2)}
\defineRow{2}{thisrow}
\rowtitle{Leaf-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{output/F2_area_leaf_dt_area_leaf_dt}{}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}m_{\textrm{t}}}$}{output/F2_area_leaf_dt_darea_leaf_dmass_live}{$\times$}
\othercol{3}{$\frac{\textrm{d}m_{\textrm{t}}}{\textrm{d}b}$}{output/F2_area_leaf_dt_fraction_allocation_growth}{$\times$}
\othercol{4}{$\frac{\textrm{d}b}{\textrm{d}t}$}{output/F2_area_leaf_dt_net_mass_production_dt}{}
\rowlabel{(3)}

\defineRow{3}{thisrow}
\rowtitle{Height growth}
\firstcol{1}{$\frac{\textrm{d}h}{\textrm{d}t}$}{output/F2_height_dt_height_dt}{}
\othercol{2}{$\frac{\textrm{d}h}{\textrm{d}a_{\textrm{l}}}$}{output/F2_height_dt_dheight_darea_leaf}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{output/F2_area_leaf_dt_area_leaf_dt}{}
\rowlabel{(4)}

\defineRow{4}{thisrow}
\rowtitle{Basal-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{output/F2_area_stem_dt_area_stem_dt}{}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{ss}}}{\textrm{d}a_{\textrm{l}}}$}{output/empty_box}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{output/F2_area_stem_dt_area_leaf_dt}{+}
\othercol{4}{$\frac{\textrm{d}a_{\textrm{sh}}}{\textrm{d}t}$}{output/F2_area_stem_dt_area_heartwood_dt}{}
\rowlabel{(5)}

\defineRow{5}{thisrow}
\rowtitle{Diameter growth}
\firstcol{1}{$\frac{\textrm{d}D}{\textrm{d}t}$}{output/F2_diameter_stem_dt_diameter_stem_dt}{}
\othercol{2}{$\frac{\sqrt{\pi}}{\sqrt{a_{\textrm{st}}}}$}{output/F2_diameter_stem_dt_ddiameter_stem_darea_stem}{$\times$}
\othercol{3}{$\frac{\textrm{d}a_{\textrm{st}}}{\textrm{d}t}$}{output/F2_diameter_stem_dt_area_stem_dt}{}
\rowlabel{(6)}

### 2016-07-28 ms/ms.tex
Manuscript in subdirectory, all outputs in "output"

\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother

@@

\begin{figure}[ht]
\centering
\includegraphics{figures/BCI_data.pdf}
\caption{\textbf{The relationship between traits and potential growth
rate varies with plant size.} For XXX species from tropical rain forest
in Panama, we estimated the potential growth rate of individual's in
each species at a series of diameters $D$, indicated along right hand
side. The size of circles in each panel indicates the number of data
points used to estimate potential growth rate. Traits values were
calculated from representative individuals in each species.
\label{f-BCI}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{figures/figure_conceptual.pdf}
\caption{\textbf{Conceptual framework for understanding size-dependent
changes in growth rate.} Hump-shaped relationship between height growth rate and
size. \label{f-conceptual}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{figures/allometry.pdf}
\caption{\textbf{Key assumptions of a functional balance and trait
trade-offs model, evaluated using global dataset.} We used the biomass and
allometry database to evaluate model assumptions about \textbf{a,}
scaling of leaf area with plant height, \textbf{b} Scaling of sapwood
area with leaf area, and \textbf{c} scaling of root mass with leaf area.
Each dot is a single plant. Lines show standardised major axis lines
fitted to data from each site, with intensity of shading adjusted
according to strength of the relationship. Colours indicate vegetation
type. Dashed black lines show values expected under functional-balance
assumption (see Supplementary text for details). \label{f-assumptions}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{figures/growth_light_dia.pdf}
\caption{\textbf{Traits moderate the responsiveness of growth to changes
in light environment (diameter growth).} Panels show predicted relationship between
specific trait and diameter growth rate, for a plant of specified
diameter and under a range of shading environments.
\label{f-growth_light_dia}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{figures/growth_light_mass.pdf}
\caption{\textbf{Traits moderate the responsiveness of growth to changes
in light environment (mass growth).} Panels show predicted relationship between
specific trait and diameter growth rate, for a plant of specified
diameter and under a range of shading environments.
\label{f-growth_light_mass}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{figures/max_leaf_above.pdf}
\caption{\textbf{The effect of traits on growth changes with size and
light environment.} Traits moderate the responsiveness of growth to changes in light
environmentThis figure needs to show more of key result with respect to to size.
Possibly separate figure. \label{f-shifts}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{figures/max_leaf_above.pdf}
\caption{\textbf{Low construction cost leads to shade intolerance,
because of costs of high turnover.} Panels show effect of traits on
maximum amount of shading that can be endured before net production (eq.
\ref{eq:dbdt}) reaches zero. Lines indicate relationship for plants of a
given height. \label{f-wplcp}}
\end{figure}

@@

\begin{table}[ht]
\caption{Model parameters}
\centering
{\footnotesize  % smaller font, double space
\begin{doublespace}
% \include{figures/table-pars}

@@

\begin{figure}[ht]
\centering
\includegraphics{figures/SI_quantile_examples.pdf}
\caption{\textbf{Estimating potential growth rate via quantile
regression.} Example for 4 species. Growth rate estimated at six sizes,
by fitting lines within given size intervals. Lines fitted to 99th
quantile, but only when n \textgreater{} 500. Except for left-hand
panel, estimated points in centre of interval.
\label{fS-quantile_examples}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{figures/SI_lma_tradeoff.pdf}
\caption{\textbf{Leaf turnover decreases with leaf-construction cost.}
Data from \citep{wright-2004} for 678 species from 51 sites, each
point giving a species-average. Lines show standardised major axis lines
fitted to data from each site, with intensity of shading adjusted
according to strength of the relationship.\label{fS-leaf}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{figures/SI_mass_fraction.pdf}
\caption{\textbf{Change in allocation with size.}
\label{f-mass_fraction}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{figures/SI_lma_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between leaf-construction cost
and growth rate changes with plant size.} \label{f-lma_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{figures/SI_lma_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between leaf-construction cost
and relative growth rate changes with plant size.}
\label{f-lma_growth_size_relative}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{figures/SI_rho_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between stem-construction cost
and growth rate changes with plant size.} \label{f-rho_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{figures/SI_rho_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between stem-construction cost
and relative growth rate changes with plant size.}
\label{f-rho_growth_size_relative}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{figures/SI_hmat_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between maximum height and
growth rate changes with plant size.} \label{f-hmat_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{figures/SI_hmat_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between maximum height and
relative growth rate changes with plant size.}
\label{f-hmat_growth_size_relative}}
\end{figure}

>>>>

\usepackage{graphicx}
\graphicspath{{../output/}}

% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother

@@

\begin{figure}[ht]
\centering
\includegraphics{BCI_data.pdf}
\caption{\textbf{The relationship between traits and potential growth
rate varies with plant size.} For XXX species from tropical rain forest
in Panama, we estimated the potential growth rate of individual's in
each species at a series of diameters $D$, indicated along right hand
side. The size of circles in each panel indicates the number of data
points used to estimate potential growth rate. Traits values were
calculated from representative individuals in each species.
\label{f-BCI}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{figure_conceptual.pdf}
\caption{\textbf{Conceptual framework for understanding size-dependent
changes in growth rate.} Hump-shaped relationship between height growth rate and
size. \label{f-conceptual}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{allometry.pdf}
\caption{\textbf{Key assumptions of a functional balance and trait
trade-offs model, evaluated using global dataset.} We used the biomass and
allometry database to evaluate model assumptions about \textbf{a,}
scaling of leaf area with plant height, \textbf{b} Scaling of sapwood
area with leaf area, and \textbf{c} scaling of root mass with leaf area.
Each dot is a single plant. Lines show standardised major axis lines
fitted to data from each site, with intensity of shading adjusted
according to strength of the relationship. Colours indicate vegetation
type. Dashed black lines show values expected under functional-balance
assumption (see Supplementary text for details). \label{f-assumptions}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{growth_light_dia.pdf}
\caption{\textbf{Traits moderate the responsiveness of growth to changes
in light environment (diameter growth).} Panels show predicted relationship between
specific trait and diameter growth rate, for a plant of specified
diameter and under a range of shading environments.
\label{f-growth_light_dia}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{growth_light_mass.pdf}
\caption{\textbf{Traits moderate the responsiveness of growth to changes
in light environment (mass growth).} Panels show predicted relationship between
specific trait and diameter growth rate, for a plant of specified
diameter and under a range of shading environments.
\label{f-growth_light_mass}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{max_leaf_above.pdf}
\caption{\textbf{The effect of traits on growth changes with size and
light environment.} Traits moderate the responsiveness of growth to changes in light
environmentThis figure needs to show more of key result with respect to to size.
Possibly separate figure. \label{f-shifts}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{max_leaf_above.pdf}
\caption{\textbf{Low construction cost leads to shade intolerance,
because of costs of high turnover.} Panels show effect of traits on
maximum amount of shading that can be endured before net production (eq.
\ref{eq:dbdt}) reaches zero. Lines indicate relationship for plants of a
given height. \label{f-wplcp}}
\end{figure}

@@

\begin{table}[ht]
\caption{Model parameters}
\centering
{\footnotesize  % smaller font, double space
\begin{doublespace}
% \include{table-pars}

@@

\begin{figure}[ht]
\centering
\includegraphics{SI_quantile_examples.pdf}
\caption{\textbf{Estimating potential growth rate via quantile
regression.} Example for 4 species. Growth rate estimated at six sizes,
by fitting lines within given size intervals. Lines fitted to 99th
quantile, but only when n \textgreater{} 500. Except for left-hand
panel, estimated points in centre of interval.
\label{fS-quantile_examples}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{SI_lma_tradeoff.pdf}
\caption{\textbf{Leaf turnover decreases with leaf-construction cost.}
Data from \citep{wright-2004} for 678 species from 51 sites, each
point giving a species-average. Lines show standardised major axis lines
fitted to data from each site, with intensity of shading adjusted
according to strength of the relationship.\label{fS-leaf}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{SI_mass_fraction.pdf}
\caption{\textbf{Change in allocation with size.}
\label{f-mass_fraction}}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics{SI_lma_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between leaf-construction cost
and growth rate changes with plant size.} \label{f-lma_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI_lma_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between leaf-construction cost
and relative growth rate changes with plant size.}
\label{f-lma_growth_size_relative}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI_rho_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between stem-construction cost
and growth rate changes with plant size.} \label{f-rho_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI_rho_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between stem-construction cost
and relative growth rate changes with plant size.}
\label{f-rho_growth_size_relative}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI_hmat_effects_at_diameters.pdf}
\caption{\textbf{The expected correlation between maximum height and
growth rate changes with plant size.} \label{f-hmat_growth_size}}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics{SI_hmat_effects_at_diameters_relative.pdf}
\caption{\textbf{The expected correlation between maximum height and
relative growth rate changes with plant size.}
\label{f-hmat_growth_size_relative}}
\end{figure}
